Article results

### 2022-07-11 analysis/article-results.Rmd
Unpenalized multivar interaction-by-cohort is better

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin
  )
)

@@

# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
```

@@

```{r valid-dev}
# Optimism correctedL
validation_dev_lambdamin$validation_summary %>% 
  filter(measure %in% c("auc", "intercept", "slope")) %>% 
  group_by(measure) %>% 
  summarise(value = paste0(corrected, " [", lower_corrected, ";", upper_corrected, "]")) %>%
  knitr::kable()
```

```{r dev-calib}
calplot_MI(
  imps_long = imps_all %>% 
    filter(imps_label == "imps_assess" & dataset == "develop"),
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 100,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

@@

# Compute linear predictor
lp_valid <- drop(predict(mod_develop, newx = X_valid))
df_calplot_valid <- cbind.data.frame(lp_valid, imps_valid)

@@

calplot_MI(
  imps_long = imps_valid,
  model = validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

@@

@@

>>>>

```{r objs}
tar_load(
  c(
    dat_combined,
    dat_to_impute,
    imps_all,
    candidate_predictors,
    model_formula,
    analysis_settings,
    validation_dev_lambdamin,
    validation_comb_lambdamin,
    validation_dev_lambda1se,
    validation_comb_lambda1se
  )
)

@@

# Visualise missings beforehand
naniar::gg_miss_var(dat_to_impute, facet = dataset, show_pct = TRUE)
naniar::gg_miss_upset(dat_valid, nsets = 10)
naniar::gg_miss_upset(dat_develop, nsets = 10)
```

@@

```{r valid-dev}
# Optimism corrected
validation_dev_lambdamin$validation_summary %>% 
  filter(measure %in% c("auc", "intercept", "slope")) %>% 
  group_by(measure) %>% 
  summarise(value = paste0(corrected, " [", lower_corrected, ";", upper_corrected, "]")) %>%
  knitr::kable()
```

```{r dev-calib}
calplot_MI(
  imps_long = imps_all %>% 
    filter(imps_label == "imps_assess" & dataset == "develop"),
  model = mod_develop_1se, #validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 100,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

@@

# 1 se test
folds <- assign_crossval_folds(y = unique(imps_develop[[".id"]]), n_folds = 10)
cross_val <- glmnet::cv.glmnet(
    x = subset(x = stats::model.matrix(model_formula, data = imps_develop), select = -`(Intercept)`),
    y = imps_develop$Mc_FailedFemoralApproach,
    wts = imps_develop$wts,
    foldid = folds[match(imps_develop[[".id"]], folds[["y"]]), "fold"],
    family = "binomial",
    alpha = 0
  )
plot(cross_val)

folds <- assign_crossval_folds(y = unique(imps_all[[".id"]]), n_folds = 10)

cross_val <- glmnet::cv.glmnet(
    x = subset(x = stats::model.matrix(model_formula, data = imps_all), select = -`(Intercept)`),
    y = imps_all$Mc_FailedFemoralApproach,
    wts = imps_all$wts,
    foldid = folds[match(imps_all[[".id"]], folds[["y"]]), "fold"],
    family = "binomial",
    alpha = 0
  )
cross_val$lambda
plot(cross_val)

mod_develop_1se <- run_stacked_glmnet(
    x = subset(x = stats::model.matrix(model_formula, data = imps_develop), select = -`(Intercept)`),
    y = imps_develop$Mc_FailedFemoralApproach,
    wts = imps_develop$wts,
    foldid = folds[match(imps_develop[[".id"]], folds[["y"]]), "fold"],
    lambda_choice = "1se",
    alpha = 0
  )

# Compute linear predictor
lp_valid <- drop(predict(mod_develop_1se, newx = X_valid))
df_calplot_valid <- cbind.data.frame(lp_valid, imps_valid)

@@

calplot_MI(
  imps_long = imps_valid,
  model = mod_develop_1se, #validation_dev_lambdamin$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 5,
  n_bins = 200,
  xlim = c(0, 0.85),
  ylim = c(-0.25, 1)
) +
  theme_minimal()
```

@@

calplot_MI(
  imps_long = imps_combined,
  model = validation_comb_lambda1se$model_fit,
  impdat_ind = ".imp",
  model_formula = model_formula,
  height_hist = 0.2,
  startpos_hist = -0.25,
  knots = 3,
  n_bins = 200,
  xlim = c(0, 0.55),
  ylim = c(-0.25, 0.8)
) +
  theme_minimal()

@@

```{r interaction-by-cohort}
split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |>  
  ggforestplot::forestplot(
    name = term,
    estimate = estimate,
    se = std.error
  )

split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  select(term, estimate)

split(imps_combined |> filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate)

cbind.data.frame(
  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  select(term, estimate),
  "develop" = split(imps_combined |> filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate),
  "valid" =  split(imps_combined |> filter(dataset == "valid"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate),
  "combined" =  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy() |> 
  pull(estimate)
) |> 
  View()

# ORs
cbind.data.frame(
  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(update(model_formula, . ~ . * dataset), family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  select(term, estimate),
  "develop" = split(imps_combined |> filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  pull(estimate),
  "valid" =  split(imps_combined |> filter(dataset == "valid"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  pull(estimate),
  "combined" =  split(imps_combined, ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  broom::tidy(exponentiate = TRUE) |> 
  pull(estimate)
) |> 
  View()

model.matrix(model_formula, data=imps_combined) %>% 
  cor(use="pairwise.complete.obs") %>% 
  ggcorrplot::ggcorrplot(show.diag = F, type="lower", lab=TRUE, lab_size=2)
```
